Lessons learned from bugs in models of human history

### 2020-08-06 paper.tex
minor tweak for clarity

Even though the error has a limited effect on simulated data, the tutorial code has been
copied many times and used in publications. By searching for some identifying strings
from the model definition on GitHub,
we found 32 repositories containing either direct copies of the
erroneous model code, or code that was obviously derived from it.
(We have opened issues on each of these repositories to alert the authors.)
In most cases the publications used simulations to test a non-demographic inference
method, such as inferring gene genealogies from sequencing data~\citep{kelleher2019inferring},
determining the age of a genetic variant~\citep{albers2020dating},
or studying the power of variant association tests~\citep{tong2020population},
and the model was used as an example of a complex population history.
\citet{zhou2018popdemog}~used the incorrect model as an example
of how their method for visualising demographic models can support
\msprime\ input.
Finally, \citet{pfaffelhuber2020choose}~used simulations
of the incorrect model demography to evaluate
their method for choosing ancestry informative markers.
Given the very subtle effect of the incorrect
model on demography (and the fact the method was evaluated using other
simulations and real data), it seems unlikely that the model details
had any qualitative effect on their conclusions.

>>>>

Even though the error has a limited effect on simulated data, the tutorial code has been
copied many times and used in publications. By searching for some identifying strings
from the model definition on GitHub,
we found 32 repositories containing either direct copies of the
erroneous model code, or code that was obviously derived from it.
(We have opened issues on each of these repositories to alert the authors.)
In most cases the publications used simulations to test a non-demographic inference
method, such as inferring gene genealogies from sequencing data~\citep{kelleher2019inferring},
determining the age of a genetic variant~\citep{albers2020dating},
or studying the power of variant association tests~\citep{tong2020population}.
In each of these studies, this model was used as an example of a complex population history.
\citet{zhou2018popdemog}~used the incorrect model as an example
of how their method for visualising demographic models can support
\msprime\ input.
Finally, \citet{pfaffelhuber2020choose}~used simulations
of the incorrect model demography to evaluate
their method for choosing ancestry informative markers.
Given the very subtle effect of the incorrect
model on demography (and the fact the method was evaluated using other
simulations and real data), it seems unlikely that the model details
had any qualitative effect on their conclusions.
